---
title: "Merged_Data"
author: "Samxie"
date: "2025-05-09"
output: html_document
---

```{r}
library(tidyverse)
library(readr)
library(stringr)
```

## Merged one by one

***1 AirBnB***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/AirBnB_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/AirBnB_comments_redditapi.csv")
```
toxic is itself-merged.
```{r}
# toxic_sentiment <- left_join(toxic, sentiment)
```
**brand_found**
```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/AirBnB_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(str_detect(comment_body, regex("AirBnB", ignore_case = TRUE)), 1, 0)
  )
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/AirBnB_comments_redditapi_merged.csv")
```

***2 amazon***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/amazon_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/amazon_comments_redditapi.csv")
```
toxic is itself-merged.
```{r}
# toxic_sentiment <- left_join(toxic, sentiment)
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/amazon_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(str_detect(comment_body, regex("amazon", ignore_case = TRUE)), 1, 0)
  )
```

```{r}
toxic_sentiment$comment_body[[1]]
```
```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/amazon_comments_redditapi_merged.csv")
```

***3 Apple***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/apple_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/apple_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/apple_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/apple_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(str_detect(comment_body, regex("Apple", ignore_case = TRUE)), 1, 0)
  )
```

```{r}
toxic_sentiment$comment_body[[5]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/apple_comments_redditapi_merged.csv")
```

***4 Blizzard***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/Blizzard_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/Blizzard_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Blizzard_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Blizzard_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(str_detect(comment_body, regex("Blizzard", ignore_case = TRUE)), 1, 0)
  )
```

```{r}
toxic_sentiment$comment_body[[1]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Blizzard_comments_redditapi_merged.csv")
```


***5 BMW - DataIssue 错行***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/BMW_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/BMW_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/BMW_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/BMW_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(str_detect(comment_body, regex("BMW", ignore_case = TRUE)), 1, 0)
  )
```

```{r}
toxic_sentiment$comment_body[[8]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/BMW_comments_redditapi_merged.csv")
```

***6 Dominos ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/Dominos_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/Dominos_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Dominos_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Dominos_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(str_detect(comment_body, regex("Dominos", ignore_case = TRUE)), 1, 0)
  )
```

```{r}
toxic_sentiment$comment_body[[27]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Dominos_comments_redditapi_merged.csv")
```

***7 EASportsUFC ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/EASportsUFC_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/EASportsUFC_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/EASportsUFC_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/EASportsUFC_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("EASportsUFC|EASports|UFC|EA", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[3]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/EASportsUFC_comments_redditapi_merged.csv")
```

***8 Ebay ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/Ebay_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/Ebay_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Ebay_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Ebay_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("Ebay", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[3]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Ebay_comments_redditapi_merged.csv")
```

***9 glossier ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/glossier_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/glossier_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/glossier_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/glossier_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("glossier", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[7]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/glossier_comments_redditapi_merged.csv")
```

***10 intel ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/intel_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/intel_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/intel_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/intel_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("intel", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[2]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/intel_comments_redditapi_merged.csv")
```

***11 McDonalds ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/McDonalds_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/McDonalds_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/McDonalds_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/McDonalds_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("McDonalds", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[1]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/McDonalds_comments_redditapi_merged.csv")
```

***12 microsoft ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/microsoft_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/microsoft_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) 
# |>  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/microsoft_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/microsoft_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("microsoft|ms", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[2]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/microsoft_comments_redditapi_merged.csv")
```

***13 mintmobile ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/mintmobile_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/mintmobile_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) 
# |>  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/mintmobile_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/mintmobile_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("mintmobile", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[3]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/mintmobile_comments_redditapi_merged.csv")
```

***14 netflix ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/netflix_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/netflix_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) 
# |>  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/netflix_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/netflix_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("netflix", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[5]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/netflix_comments_redditapi_merged.csv")
```

***15 NintendoSwitch ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/NintendoSwitch_commets_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/NintendoSwitch_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) 
# |>  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/NintendoSwitch_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/NintendoSwitch_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("NintendoSwitch|Nintendo|Switch", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[15]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/NintendoSwitch_comments_redditapi_merged.csv")
```

***16 nvidia ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/nvidia_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/nvidia_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>  
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/nvidia_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/nvidia_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("nvidia", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[3]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/nvidia_comments_redditapi_merged.csv")
```

***17 paypal ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/paypal_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/paypal_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>  
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/paypal_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/paypal_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("paypal", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[7]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/paypal_comments_redditapi_merged.csv")
```

***18 peloton ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/peloton_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/peloton_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>  
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/peloton_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/peloton_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("peloton", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[18]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/peloton_comments_redditapi_merged.csv")
```

***19 playstation ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/playstation_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/playstation_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>  
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/playstation_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/playstation_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("playstation|ps4|ps5", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[10]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/playstation_comments_redditapi_merged.csv")
```


***20 QuickBooks ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/QuickBooks_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/QuickBooks_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>  
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/QuickBooks_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/QuickBooks_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("QuickBooks", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[2]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/QuickBooks_comments_redditapi_merged.csv")
```

***21 razer ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/razer_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/razer_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/razer_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/razer_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("razer", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[8]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/razer_comments_redditapi_merged.csv")
```


***22 RobinHood ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/RobinHood_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/RobinHood_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/RobinHood_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/RobinHood_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("RobinHood", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[25]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/RobinHood_comments_redditapi_merged.csv")
```


***23 spotify ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/spotify_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/spotify_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/spotify_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/spotify_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("spotify", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[12]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/spotify_comments_redditapi_merged.csv")
```

***24 starbucks ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/starbucks_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/starbucks_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/starbucks_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/starbucks_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("starbucks|starbuck", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[2]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/starbucks_comments_redditapi_merged.csv")
```

***25 Steam ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/Steam_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/Steam_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic, by=c("comment_id"))
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(-post_id.y, -author.y, -created_utc.y, -comment_body.y, -score.y)
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  rename_with(~ sub("\\.x$", "", .), ends_with(".x"))
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Steam_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Steam_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("Steam", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[2]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Steam_comments_redditapi_merged.csv")
```

***26 supremeclothing ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/supremeclothing_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/supremeclothing_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/supremeclothing_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/supremeclothing_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("supremeclothing|supreme", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[5]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/supremeclothing_comments_redditapi_merged.csv")
```

***27 tacobell ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/tacobell_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/tacobell_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/tacobell_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/tacobell_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("tacobell", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[3]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/tacobell_comments_redditapi_merged.csv")
```

***28 teslamotors ***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/teslamotors_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/teslamotors_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/teslamotors_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/teslamotors_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("teslamotors|tesla", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[10]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/teslamotors_comments_redditapi_merged.csv")
```

***29 Toyota***
```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/Toyota_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/Toyota_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Toyota_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Toyota_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("Toyota", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[1]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/Toyota_comments_redditapi_merged.csv")
```

***30 xbox***

```{r include=FALSE}
toxic <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/Toxic_api/xbox_comments_redditapi.csv")
sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/sentiment_api/xbox_comments_redditapi.csv")
```

```{r}
toxic_sentiment <- left_join(sentiment, toxic) |>
  select(-1)
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/xbox_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- read_csv("/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/xbox_comments_redditapi_merged.csv")
```

```{r}
toxic_sentiment <- toxic_sentiment |>
  select(1:15) |>
  mutate(
    brand_found = ifelse(
      str_detect(comment_body, regex("xbox", ignore_case = TRUE)),
      1, 0
    )
  )
```

```{r}
toxic_sentiment$comment_body[[3]]
```

```{r}
write_csv(toxic_sentiment, "/Users/samxie/Research/HEC/Reddit\ Merge\ 0509/merged_sentiment_toxic/xbox_comments_redditapi_merged.csv")
```
